---
title: "Your Second App"
author: "Brian Caffo"
date: "6/19/2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

## Basic app
- We're going to create a basic app that just communicates
betwen R and the alexa service
- We'll use the plumber server that you created in the previous
lecture

## Save this file 
- In a directory called `alexaTest/plumber.R`
- [file here](https://github.com/bcaffo/alexaai/tree/master/lectures/05_your_2nd_app/alexaTest)

```{r}
library(alexar)

#* @post /
#* @serializer unboxedJSON
function(req){
  dispatchAlexaRequest(req, intent=function(name, slots, ...){
    if (name=="askIntent"){
      alexaResponse(output="Thank you for asking, but try with some manners!")
    } else if (name=="pleaseIntent"){
      alexaResponse(output="You said the magic word!")
    }
  }, launch=function(){
    alexaResponse("You can ask to test the app, try using please")
  })
}

```


## Getting your service running
```{r}
## list out your droplets
analogsea::droplets()
## assign the one you want to a variable
myDroplet = analogsea::droplets()$alexatest
```
- `alexatest` is the name of my droplet (also what I'm calling the app and plumber service)


## Remove the hello app if you installed it

```{r}
do_remove_forward(myDroplet)
do_remove_api(myDroplet, "hello", delete = TRUE)
```

## Install `alexar` on the server

- either log onto the server and install it from github using devtools
- or use `analogsea` in R from your local computer 
```{r}
analogsea::droplet_ssh(myDroplet, "Rscript -e \"devtools::install_github('DataScienceSpecialization/alexar')\"")
```


## Run your service

```{r}
do_deploy_api(droplet = myDroplet, 
              path = "alexaTest/",  
              localPath = "alexaTest", 
              forward = TRUE, 
              port = 8000)
```
- `droplet` the droplet object obtained previously
- `path` remote path to your `plumber.R` file (mine is then in `/var/plumber/alexatest`)
- `localPath` local path to your directory with `plumber.R` in it
- `forward` whether traffic from the root ip is forwarded
- `port` the internet protocol port, keep at 8000

## Verify it on your server
- ssh into your server and type
```
systemctl status plumber-alexaTest.service 
```
(replace `alexaTest` with the name of your service)

```
● plumber-alexaTest.service - Plumber API
   Loaded: loaded (/etc/systemd/system/plumber-alexaTest.service; enabled; vendor preset: enabled)
   Active: active (running) since Mon 2017-06-19 23:17:09 UTC; 3s ago
 Main PID: 16041 (R)
   CGroup: /system.slice/plumber-alexaTest.service
           └─16041 /usr/lib/R/bin/exec/R --slave --no-restore -e pr~+~<-~+~plumber::plumb('/var/plumber/alexaTest/plumber.R');~+~~+~pr$run(port=8000)

Jun 19 23:17:09 alexatest systemd[1]: Stopped Plumber API.
Jun 19 23:17:09 alexatest systemd[1]: Started Plumber API.
Jun 19 23:17:10 alexatest Rscript[16041]: Starting server to listen on port 8000
```

## Creating your app on alexa skills kit
- We've already gone over much of this, so we'll redo it kind of quickly
- Go to Amazon Developer Console -> Alexa -> Add new skill
- Skill type should be "Custom interaction model"
- Fill in the rest of the fields, click Save then Next

## My entries
- `Name = plumberTestApp`
- `Invocation name = test plumber`
- `Audio player = no`


## My intent schema

```
{
  "intents": [
    {
      "intent": "askIntent"
    },
    {
      "intent": "pleaseIntent"
    }
  ]
}
```

## Sample utterances
```
askIntent test my app
askIntent can you test my app
askIntent will you test my app
pleaseIntent will you please test my app
pleaseIntent please test my app
```

## Configuration
- Pick Endpoint as `https`
- Pick the appropriate region
- Enter your domain, mine was
`https://myalexaservice.site/alexaTest/`

## Verify ssl cert
`My development endpoint has a certificate from a trusted certificate authority`

## Test your app
- Test your app using the alexa skills kit testing service
- Your app should be sending back the correct json files for the
the request
- You can download the app onto your (own) Echo using the app
- To get it so that everyone can download it, you have to complete
the certification process through amazon (don't bother for this simple app)
- Congrats!

## Manually setting up the server
- I have some scripts for setting up your server from the command prompt
(on the server)
- You can find the scripts [here](https://github.com/bcaffo/digitalOceanScripts)




