---
title: "Your third app"
author: "Brian Caffo"
date: "6/27/2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

## A full app
- In this lecture, we'll build our first (sort of) useful app
- It will be a lecture that gives fake Jeff Leek facts (or are they real?)
- Uses code developed by Jeff Allen
- We want to be able to do Alexa "load jeff leek facts", then "tell me a jeff leek fact"
to tell us a fact
- First clone `alexar` locally
```
git clone https://github.com/jhudsl/alexar.git
```

## Provision a server
- Assume that you're starting fresh
- Provision a server (lecture 3)
- Set up SSL (lecture 4)
- Install needed packages on your server, you can do this with `analogsea`
from your local computer
```{r}
analogsea::droplet_ssh(myDroplet, "Rscript -e \"devtools::install_github('wlandau/JeffLeekMeme')\"")
analogsea::droplet_ssh(myDroplet, "Rscript -e \"devtools::install_github('DataScienceSpecialization/alexar')\"")
```
(or you can log onto your server over ssh and do it there)
```
Rscript -e "devtools::install_github('wlandau/JeffLeekMeme')"
Rscript -e "devtools::install_github('DataScienceSpecialization/alexar')"
```

## Deploy your api
- I cloned `alexar` locally 
`git clone https://github.com/jhudsl/alexar.git`
- I deployed with this command:
```{r}
do_deploy_api(droplet = myDroplet, 
              path = "jeffleekfacts/",  
              localPath = "~/sandboxes/alexar/inst/examples/01-jeffleek/", 
              forward = TRUE, 
              port = 8000)
```


## Intent schema
We'll use our intent schema from the same app built using lambda
```
{
  "intents": [
    {
      "intent": "tellfact"
    },
    {
      "intent": "AMAZON.HelpIntent"
    },
    {
      "intent": "AMAZON.StopIntent"
    },
    {
      "intent": "AMAZON.CancelIntent"
    }
  ]
}
```

## Sample utterances
```
tellfact a fact
tellfact a Jeff fact
tellfact tell me a Jeff fact
tellfact tell me a Jeff fact
tellfact give me a fact
tellfact give me a Jeff fact
tellfact tell me Jeff Leek fact
```

## Make sure that your site is connected via https
- Make sure that you went through the same steps
in our previous app to connect your server over https

## Some useful commands
Stop the app
```
systemctl stop plumber-jeffleekfacts
```
Restart the app
```
systemctl restart plumber-jeffleekfacts
```
Watch the app interaction
```
journalctl -u plumber-jeffleekfacts
```

## Roughly, what is do_deploy_api doing?
- This is not necessary, but it helps us understand what `do_deploy_api`
is doing
- In the next few slides, we'll cover the basics
- We'll structure it as if you were to deploy the same app manually

##  Copy your  api files to the relevant system directory
```{sh}
mkdir -p /var/plumber/jeffleekfacts
cp -r /usr/local/lib/R/site-library/alexar/examples/01-jeffleek/* /var/plumber/jeffleekfacts/
cp /usr/local/lib/R/site-library/plumber/server/plumber.service /etc/systemd/system/plumber-jeffleekfacts.service
```

## Restart the daemon
```{sh}
systemctl daemon-reload
systemctl start plumber-jeffleekfacts.service && sleep 1
systemctl restart plumber-jeffleekfacts.service && sleep 1
systemctl enable plumber-jeffleekfacts.service
# check the status
systemctl status
```

## Copy over the config file
```{sh}
conf=/usr/local/lib/R/site-library/plumber/server/plumber-api.conf
cp $conf /etc/nginx/sites-available/plumber-apis/jeffleekfacts.conf
systemctl reload nginx
```


